\addcontentsline{toc}{chapter}{СПИСОК ИСПОЛЬЗОВАННЫХ ИСТОЧНИКОВ}
\begin{thebibliography}{}
	\vspace{-1\baselineskip}

\bibitem{kaji} Kaji, S., Ochiai, H. A Concise Parametrization of Affine Transformation / SIAM Journal on Imaging Sciences. --- 2016. --- Vol. 9, No. 3. --- Pp. 1355--1372.

\bibitem{rogers_mathematical} Rogers, D. F. Mathematical Elements for Computer Graphics / D. F. Rogers, J. A. Adams. --- New York: McGraw-Hill, 1990. --- Pp. 15--87.

\bibitem{rogers_computer_graphics} Rogers, D. F. Procedural Elements for Computer Graphics / D. F. Rogers. --- New York: McGraw-Hill, 1985. --- Pp. 123--215.

\bibitem{phong_model} Phong, Bui Tuong. Illumination for computer generated pictures / Communications of the ACM. --- 1975. --- Vol.18, No.6. --- Pp. 311--317.

\bibitem{gouraud_shading} Gouraud, Henri. Continuous shading of curved surfaces / IEEE Transactions on computers. --- 1971. --- Vol.20, No.6. --- Pp. 623--629.

\bibitem{whitted_raytracing} Whitted, Turner. An improved illumination model for shaded display / Communications of the ACM. --- 1980. --- Vol.23, No.6. --- Pp. 343--349.

\bibitem{realtime_rendering} Akenine-Möller, Tomas. Real-time rendering / AK Peters/CRC Press. --- 2018. --- 1198 p.

\bibitem{shadow_mapping_technique} Williams, Lance. Casting curved shadows on curved surfaces / ACM SIGGRAPH Computer Graphics. --- 1978. --- Vol.12, No.3. --- Pp. 270--274.

\bibitem{arch_wiki} ArchWiki --- Arch Linux. Главная страница. [Электронный ресурс]. Режим доступа: https://wiki.archlinux.org/title/Main\_page (дата обращения: \today).
	
\bibitem{ryzen} AMD Ryzen™ 7 8745HX Mobile Processor. [Электронный ресурс]. -- Режим доступа: https://www.amd.com/en/products/processors/laptop/ryzen/8000-series/amd-ryzen-7-8745hx.html-- (дата обращения: \today).

\bibitem{fowler_refactoring} Fowler, M. Refactoring: Improving the Design of Existing Code / Addison-Wesley Professional. --- 2018. --- Pp. 45--98.

\bibitem{booch_uml} Booch, G., Rumbaugh, J., Jacobson, I. The Unified Modeling Language User Guide / Addison-Wesley Professional. --- 2005. --- Pp. 132--156.

\bibitem{cpp20_features} ISO/IEC 14882:2020. Programming languages --- C++ / International Organization for Standardization. --- 2020. --- 1853 p.

\bibitem{qt_documentation} The Qt Company. Qt 6.5 Documentation / Qt Documentation. --- 2023. --- Режим доступа: https://doc.qt.io/qt-6/ (дата обращения: \today).

\bibitem{vscode_debug} Microsoft Corporation. Debugging in Visual Studio Code / VS Code Docs. --- 2023. --- Режим доступа: https://code.visualstudio.com/docs/ (дата обращения: \today).

\bibitem{openmp60} OpenMP Architecture Review Board. OpenMP Application Program Interface Specification Version 6.0 / OpenMP.org. --- 2024. --- Режим доступа: https://www.openmp.org/wp-content/uploads/OpenMP-API-Specification-6-0.pdf (дата обращения: \today).


\end{thebibliography}